---
title: "WUP_04"
author: "Sylvia Rodriguez"
date: "fall 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
WordData=read_csv("GSScsv.csv")

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(WordData,aes(x=DEGREE,y=WORDSUM))

basicCN + geom_boxplot()
```

The boxplot shows us that the longer the student is in school the higher their WORDSUM. It also showed that the median for graduate scored at abou 11.5.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=WordData)
```

The median of the graduates is the highest at 11 WORDSUM and mean is also highest for them at 10.1. We can see that based off those numbers, graduates are best off.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=WordData)
summary.aov(model1)
```

The P value is very low at 0.000236. I reject the null hypothesis because the number is so low that the probability of getting the result we found is too low. 

```{r}
plot(TukeyHSD(model1))
```

The majority of those with a high school or junior college degree are below the mean in confidence leve;. This shows that they may more likely be more confident if they got a higher degree. 
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We reject the null hypothesis because the P value is very low. We found that there is a difference between LT highschool graduates and highschool graduates. 